Poster Data Analysis

### 2018-09-08 notebooks/poster_analysis.Rmd
added tables for sample information

@@

@@

```{r, fig.width = 10, fig.height=30}
species_data <- select(isolate_data, c(id, species))

megares_long <- megares_results %>%
  gather(gene, value, -c(id, type))

>>>>

species_data <- select(isolate_data, c(id, species))

@@

# Tables

## Samples per species
```{r}
per_species <- isolate_data %>%
  group_by(species) %>%
  count()
per_species
```

## Samples per sequencing method
```{r}
per_seq <- isolate_data %>%
  group_by(sequencer, libprep, read_length) %>%
  count()
per_seq
```

## MLST Data

### Total MLST 
```{r}
total_mlst <- mlst_results %>%
  left_join(species_data, by = "id") %>%
  group_by(ST) %>%
  count()
total_mlst
```

### MLST per animal species
```{r}
mlst_per_species <- mlst_results %>%
  left_join(species_data, by = "id") %>%
  group_by(ST, species) %>%
  count()
mlst_per_species
```

@@

```{r fig.height=30, fig.width=10, message=FALSE, warning=FALSE}
megares_long <- megares_results %>%
  gather(gene, value, -c(id, type))
